Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-08-04 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] updated journal version in one reference + revision of footnote 1

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and scalar
couplings has been presented in \cite{Bobeth:2007dw, Bobeth:2012vn}, adopting
the effective theory \refeq{eq:Heff}, i.e. neglecting higher dimensional operators
with \christoph{$\mbox{dim} \geq 8$}. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2} 
    \christoph{\bigg/ \Gamma_\ell} \,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests. 
The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed \christoph{by small 
lepton masses for the considered kinematical region $1 \leq q^2 \leq 22$ GeV$^2$}
\cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.  
Nonzero values of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED 
corrections, which will modify the simple $\cos\theta_\ell$ dependence of the angular
distribution~\refeq{eq:ang-distr}, however, currently there is no solid estimate
available for this source of SM background\footnote{The leading QED corrections
  to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
  corresponding effects in $B\to K \bar\ell\ell$.}. \todo{David's comment?!}

>>>>

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and scalar
couplings has been presented in \cite{Bobeth:2007dw, Bobeth:2012vn}, adopting
the effective theory \refeq{eq:Heff}, i.e. neglecting higher dimensional operators
with \christoph{$\mbox{dim} \geq 8$}. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2} 
    \christoph{\bigg/ \Gamma_\ell} \,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests. 
The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed \christoph{by small 
lepton masses for the considered kinematical region $1 \leq q^2 \leq 22$ GeV$^2$}
\cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.  
Nonzero values of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED 
corrections, which will modify the simple $\cos\theta_\ell$ dependence of the angular
distribution~\refeq{eq:ang-distr}, however, currently there is no solid estimate
available for this source of SM background\footnote{The \christoph{logarithmically
enhanced NLO QED corrections}
  to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
  corresponding effects in $B\to K \bar\ell\ell$.}. \todo{David's comment?!}
